BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-18 tex/1-intro.tex
Up

We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates. Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments. Our contributions can be summarized as follows:

>>>>

This paper presents the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates. Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments. Our contributions can be summarized as follows:

### 2014-01-18 tex/3-architecture.tex
Up

This section provides an overview of the crawler system architecture and the different techniques we used. The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. Finally, we talk about the design choices we made in view of a large scale deployment.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog. After being downloaded and identified as blog posts (details in \autoref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
\begin{enumerate}
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download multimedia files
  \item Propagate resulting records to the back end
\end{enumerate}
This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}. The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.

>>>>

This section provides an overview \TODO{issue with subsection name} of the crawler system architecture and the different techniques we used. The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. Finally, we talk about the design choices we made in view of a large scale deployment.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog. After being downloaded and identified as blog posts (details in \autoref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
\begin{enumerate}
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download multimedia files
  \item Propagate resulting records to the back end
\end{enumerate}
This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}. The BlogForever Crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.

### 2014-01-18 tex/5-related-work.tex
Important reformulations
Up

\section{Related work}

Research on large scale distributed crawler such as Mercator \cite{najork2001}, used by AltaVista, the spider discussed in \cite{shkapenyuk2002} or UbiCrawler \cite{boldi2003} are enlightening regarding the difficulties arising when scale out a crawler. One of the core issues seems to be in sharing the list URLs which have already been visited and need to be visited. While \cite{najork2001} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing. Both of these approaches require complex mechanisms to achieve fault tolerance. The BlogForever crawler circumvent this problem by delegating all state the back-end system. This shared nothing architecture between crawler instance is made possible by the fact that our unit of computations, crawling a entire blog, is much large than fetching a single URL and does not generate further crawling tasks. In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side. This removes one layer of complexity when compared to general crawler which need use a distributed file system or implement an aggregation mechanism in order to further use the collected data.

@@

>>>>

\section{Related work}
\label{relatedwork}

Web crawling has been a well-studied topic over the last decade. One direction of study which we believe to be of crucial importance is the one of large scale distributed crawlers. Our design is influenced by the work Heydon and Najork work on Mercator \cite{heydon99mercator}, Boldi et al. work's on UbiCrawler \cite{boldi2003} and Shkapenyuk and Suel work's on their spider discussed in \cite{shkapenyuk2002}. One of the core issues when scaling out a crawler seems to be in sharing the list URLs that have already been visited and need to be visited next. While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing. Both of these approaches require complex mechanisms to achieve fault tolerance.

The BlogForever Crawler -circumvent- delegates this problem by delegating all state the back-end system. This shared nothing architecture between crawler instance is made possible by the fact that our unit of computations, crawling a entire blog, is much large than fetching a single URL and does not generate further crawling tasks. In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side. This removes one layer of complexity when compared to general crawler which need use a distributed file system or implement an aggregation mechanism in order to further use the collected data.

@@

Several experiments have been conducted in

There have been several successful research working design distributed crawlers
